---
title: "Persuasion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Explore Dialogue
First load the file and libraries.
```{r}
library(readr)
library(ggplot2)
```


When loading the files, remember to change the path to the directories in your computer.
```{r, include=FALSE }
Dialogue <- read_csv("Dialogue.csv")
Dialogue$strategy <- substr(Dialogue$q_id,1,2)
dems <- read_csv("Demographics.csv")
post <- read_csv("PostQuestions.csv")
visited <- read_csv("visitedtaichi.csv")
```

### Cleaning the data
Many people started the interaction but did not finish.Therefore `dems` will be cleaned up and stored in a variable called `pre.good`

```{r}
# Exclude ppl that did not finish.
pre.good<-dems[dems$sessionID %in% post$sessionID,]
# Exclude test users
pre.good<-pre.good[pre.good$userType!="test",]
post<-post[post$sessionID %in% pre.good$sessionID,]

#Exclude those before Feb 23
pp<-Dialogue[Dialogue$sessionID %in% pre.good$sessionID,c("time","sessionID")]
pp.beforeFeb <- pp[c(67:2202),]
pre.good.sid<-unique(unlist(pre.good$sessionID, use.names = FALSE))
Dialogue <- Dialogue[Dialogue$sessionID %in% pre.good$sessionID,]
#View(pre.good)
```

We can also assign variables based on computations. For example, I will assign a number for the average **TaiChi interest** in the pre-survey, and one for the post-survey. Then I will plot them.
```{r}
interest.pre <- mean(dems$taichi_interest)
interest.post<- mean(post$taichi_learn)
barplot(c(interest.pre,interest.post))
d <- cbind(c("Pre","Post"),c(interest.pre,interest.post))
```

And then, a prettier plot:
```{r}
qplot(x=c("Pre","Post"),weight=c(interest.pre,interest.post),xlab="Survey")
```
And a t-test:
```{r}
t.test(pre.good$taichi_interest,post$taichi_learn,paired=TRUE)
```
###More complicated selections of variables
Let's see what is the usage of strategies in one user (identified by session ID.)

```{r}
barplot(table(Dialogue$strategy[Dialogue$sessionID=="ceprtq01ps0n5q92h8r74emid4" & Dialogue$speaker=="U"]))
```

Did the system understand the users?
```{r}
qplot(data=post, x=guru_understanding, binwidth=1, xlab="1=Strongly Disagree, 5=Totally agree",main="HG Understood me")
```

###Running previous research analyisis on new data

Creating Print and visited group variables
```{r}
visited.pre <- pre.good[pre.good$ID %in% visited$ID,]
visited.post <- post[post$sessionID %in% visited.pre$sessionID,]
visited.dialogues <- Dialogue[Dialogue$sessionID %in% visited.pre$sessionID,]
```

Creating Print group variables
```{r}
printed.post <- post[post$printed_flyer==1,]
printed.pre <- pre.good[pre.good$sessionID %in% printed.post$sessionID,]
printed.dialogues <- Dialogue[Dialogue$sessionID %in% printed.post$sessionID,]
```

How many people printed?
```{r}
length(printed.pre$sessionID)
```

What percentage of people printed
```{r}
length(printed.pre$sessionID)/length(pre.good$sessionID) * 100
```

Demographics stats - Now we check basic demographics: Grad/U-Grad/Staff; Ethnicity and Gender.

#### Position
* 1:U-grad
* 2:Grad
* 3:Faculty
* 4:Staff

#### Age
* 1:18-21
* 2:22-25
* 3:26-30
* 4:31-40
* 5:41-50
* 6:51-60
* 7:61+

#### Ethnicity
* 1:Caucasian
* 2:Hispanic/Latino
* 3:Middle Eastern
* 4:Asian Pacific Islander
* 5: Black/African American
* 6:Other

```{r}
table(pre.good$position)
table(pre.good$gender)
table(pre.good$ethnicity)
table(pre.good$age_range)
```

Now, in percentages:
```{r}
table(pre.good$position)/length(pre.good$position)
table(pre.good$gender)/length(pre.good$gender)
table(pre.good$ethnicity)/length(pre.good$ethnicity)
table(pre.good$age_range)/length(pre.good$age_range)
```

What percentage of people were under 40 years old?
```{r}
 length(pre.good[pre.good$age_range<5,]$sessionID)/length(pre.good$sessionID)*100
```

What was the modal age range?
```{r}
tail(names(sort(table(pre.good$age_range))), 1)
```

Compare post and pre chat desire to do excercise
```{r}
pre.desire <- pre.good$excercise_need
post.desire <- - post$post_excercise_need
t.test(pre.desire,post.desire,paired=TRUE)
```

Compare post and pre chat interest in learning taichi

```{r}
pre.interest <- pre.good$taichi_interest
post.interest <- - post$taichi_learn
t.test(pre.interest,post.interest,paired=TRUE)
```

Taichi interest table

```{r}
raw_merged = merge(x = pre.good, y = post, by = "sessionID", all = TRUE)

printed.decreased.interest <- length(raw_merged[raw_merged$taichi_learn < raw_merged$taichi_interest & raw_merged$printed_flyer == 1,]$sessionID)

printed.increased.interest <- length(raw_merged[raw_merged$taichi_learn > raw_merged$taichi_interest & raw_merged$printed_flyer == 1,]$sessionID)

printed.same.interest <- length(raw_merged[raw_merged$taichi_learn == raw_merged$taichi_interest & raw_merged$printed_flyer == 1,]$sessionID)

nprinted.decreased.interest <- length(raw_merged[raw_merged$taichi_learn < raw_merged$taichi_interest & raw_merged$printed_flyer == 0,]$sessionID)

nprinted.increased.interest <- length(raw_merged[raw_merged$taichi_learn > raw_merged$taichi_interest & raw_merged$printed_flyer == 0,]$sessionID)

nprinted.same.interest <- length(raw_merged[raw_merged$taichi_learn == raw_merged$taichi_interest & raw_merged$printed_flyer == 0,]$sessionID)

c1 <- c("", "Decreased", "Remained Same", "Increased", "Total")

c2 <- c ("No", nprinted.decreased.interest, nprinted.same.interest, nprinted.increased.interest, nprinted.decreased.interest + nprinted.same.interest + nprinted.increased.interest)

c3 <- c ("Yes", printed.decreased.interest, printed.same.interest, printed.increased.interest, printed.decreased.interest + printed.same.interest + printed.increased.interest)

c4 <- c ("Total", printed.decreased.interest + nprinted.decreased.interest, printed.same.interest + nprinted.same.interest, printed.increased.interest+nprinted.increased.interest, length(pre.good$sessionID))

print.interest <- data.frame(c1, c2, c3, c4) 
View(print.interest)
```

Creating PINT Group variables

```{r}
pint.merged <-raw_merged[raw_merged$taichi_learn > raw_merged$taichi_interest & raw_merged$printed_flyer == 1,]
```

Creating nonPINT Group variables
```{r}
npint.merged <-raw_merged[raw_merged$taichi_learn <= raw_merged$taichi_interest |  raw_merged$printed_flyer == 0,]
```

Out of the people who printed, how many had an increased interest in taichi post chat?
```{r}
length(pint.merged$sessionID)
length(printed.pre$sessionID)
```

Out of the people who printed, what was the percentage of people who had an increased interest in taichi post chat?
```{r}
length(pint.merged$sessionID)/length(printed.pre$sessionID) * 100
```

Was there a significant difference between PINT and non-PINT groups' pre chat taichi interest?

```{r}
t.test(pint.merged$taichi_interest, npint.merged$taichi_interest)
```

Was there a significant difference between PINT and non-PINT groups' post chat taichi interest?
```{r}
t.test(pint.merged$taichi_learn, npint.merged$taichi_learn)
```


Was there a significant difference between the percentages of EN utterences in PINT and non-PINT groups?

Was there a significant difference between the percentages of RN utterences in PINT and non-Pint groups?

```{r}
pint.en <- c()
npint.en <- c()
pint.rn <- c()
npint.rn <- c()
for (s in pint.merged$sessionID) {
  totalDialogues <- length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG",])

  pint.en <- append(pint.en,(length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG" & substr(Dialogue$q_id, 1, 2) == "EN",]$sessionID))/ totalDialogues)
  
   pint.rn <- append(pint.rn,(length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG" & substr(Dialogue$q_id, 1, 2) == "RN",]$sessionID))/ totalDialogues)
}

for (s in npint.merged$sessionID) {
  totalDialogues <- length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG",])

  npint.en <- append(npint.en,(length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG" & substr(Dialogue$q_id, 1, 2) == "EN",]$sessionID))/ totalDialogues)
  
   npint.rn <- append(npint.rn,(length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG" & substr(Dialogue$q_id, 1, 2) == "RN",]$sessionID))/ totalDialogues)
}

t.test(pint.en, npint.en)
t.test(pint.rn, npint.rn)
```

Find the correlation between the number of EN,EP,RP,RN utterences and pre and post taichi chat interest
```{r}
  en.count <- c()
  ep.count <- c()
  rp.count <- c()
  rn.count <- c()
for (s in  raw_merged$sessionID) {
  en.count <- append(en.count,length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG" & substr(Dialogue$q_id, 1, 2) == "EN",]$sessionID))
  rn.count <- append(rn.count,length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG" & substr(Dialogue$q_id, 1, 2) == "RN",]$sessionID))
  ep.count <- append(ep.count,length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG" & substr(Dialogue$q_id, 1, 2) == "EP",]$sessionID))
  rp.count <- append(rp.count,length(Dialogue[Dialogue$sessionID == s & Dialogue$speaker=="HG" & substr(Dialogue$q_id, 1, 2) == "RP",]$sessionID))
}


  cor.test(ep.count, raw_merged$taichi_interest)
  cor.test(rp.count, raw_merged$taichi_interest)
  cor.test(en.count, raw_merged$taichi_interest)
  cor.test(rn.count, raw_merged$taichi_interest)
  
  cor.test(ep.count, raw_merged$taichi_learn)
  cor.test(rp.count, raw_merged$taichi_learn)
  cor.test(en.count, raw_merged$taichi_learn)
  cor.test(rn.count, raw_merged$taichi_learn)

```


```{r}
Strategy <- c("EP", "RP", "EN", "RN" )
Taichi.Interest.pre <- c(-0.2744292,0.1919599,-0.1324932,0.2541909 )
Taichi.Interest.post <- c(-0.4554372,0.1109431,-0.3339051,0.245545)
df <- data.frame(Strategy,Taichi.Interest.pre, Taichi.Interest.post)
knitr::kable(head(df))
```

+ greater

```{r}
  interest.increase <-raw_merged$taichi_learn - raw_merged$taichi_interest
  cor.test(ep.count, interest.increase)
  cor.test(rp.count, interest.increase)
  cor.test(en.count, interest.increase)
  cor.test(rn.count, interest.increase)
```