---
title: "Persuasion"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Explore Dialogue
First load the file and libraries.
```{r}
library(readr)
library(ggplot2)
```
When loading the files, remember to change the path to the directories in your computer.
```{r, include=FALSE }
Dialogue <- read_csv("Dialogue.csv")
Dialogue$strategy <- substr(Dialogue$q_id,1,2)
dems <- read_csv("Demographics.csv")
post <- read_csv("PostQuestions.csv")
```

### Cleaning the data
Many people started the interaction but did not finish.Therefore `dems` will be cleaned up and stored in a variable called `pre.good`

```{r}
# Exclude ppl that did not finish.
pre.good<-dems[dems$sessionID %in% post$sessionID,]
# Exclude test users
pre.good<-pre.good[pre.good$userType!="test",]
post<-post[post$sessionID %in% pre.good$sessionID,]

#Exclude those before Feb 23
pp<-Dialogue[Dialogue$sessionID %in% pre.good$sessionID,c("time","sessionID")]
pp.beforeFeb <- pp[c(34,length(pp$time)),]
pre.good.sid<-unique(unlist(pre.good$sessionID, use.names = FALSE))

#View(pre.good)
```

Now we check basic demographics: Grad/U-Grad/Staff; Ethnicity and Gender.

#### Position
* 1:U-grad
* 2:Grad
* 3:Faculty
* 4:Staff

#### Age
* 1:18-21
* 2:22-25
* 3:26-30
* 4:31-40
* 5:41-50
* 6:51-60
* 7:61+

#### Ethnicity
* 1:Caucasian
* 2:Hispanic/Latino
* 3:Middle Eastern
* 4:Asian Pacific Islander
* 5: Black/African American
* 6:Other
```{r}
table(pre.good$position)
table(pre.good$gender)
table(pre.good$ethnicity)
table(pre.good$age_range)
```

Now, in percentages:
```{r}
table(pre.good$position)/length(pre.good$position)
table(pre.good$gender)/length(pre.good$gender)
table(pre.good$ethnicity)/length(pre.good$ethnicity)
table(pre.good$age_range)/length(pre.good$age_range)
```

We can also assign variables based on computations. For example, I will assign a number for the average **TaiChi interest** in the pre-survey, and one for the post-survey. Then I will plot them.
```{r}
interest.pre <- mean(pre.good$taichi_interest)
interest.post<- mean(post$taichi_learn)
barplot(c(interest.pre,interest.post))
d <- rbind(c("Pre","Post"),c(interest.pre,interest.post))
```

And then, a prettier plot:
```{r}
qplot(x=c("Pre","Post"),weight=c(interest.pre,interest.post),xlab="Survey")
```
And a t-test:
```{r}
t.test(pre.good$taichi_interest,post$taichi_learn,paired=TRUE)
```
###More complicated selections of variables
Let's see what is the usage of strategies in one user (identified by session ID.)

```{r}
barplot(table(Dialogue$strategy[Dialogue$sessionID=="ceprtq01ps0n5q92h8r74emid4" & Dialogue$speaker=="U"]))
```

Did the system understand the users?
```{r}
qplot(data=post, x=guru_understanding, binwidth=1, xlab="1=Strongly Disagree, 5=Totally agree",main="HG Understood me")
```



